Verifying Demonstrations

### 2017-09-28 SystemModel.tex
Generalizes, clarifies strength function
This fixes a part of #25, #26.

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \interval{0}{1}\) and 
  a threshold \(\theta\).
\end{definition}

>>>>

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(id\) as the 
  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
      j = id, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}

The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
A trivial example would be for \(s\) to return the number of witnesses and thus 
let \(\theta\) to be the threshold of the number of required witnesses.
